# Model input parameters
## Raw input data
```{r}
library(dplyr)
library(ggplot2)

showTransportInputMultiLinePlots <- function(data, vars, scales = "free_y", nrowNum = 1, mainReg = getOption("mip.mainReg")) {
  
  # Validate function arguments
  stopifnot(is.character(vars))
  stopifnot(is.character(scales) && length(scales) == 1)
  stopifnot(is.character(mainReg) && length(mainReg) == 1)
  
  # Data preprocessing
  d <- data %>%
    filter(variable %in% vars) %>%
    droplevels()
  
  dMainScen <- d %>%
    filter(region == mainReg, scenario != "historical") %>%
    droplevels()
  
  dMainHist <- d %>%
    filter(region == mainReg, scenario == "historical") %>%
    droplevels()
  
  dRegiScen <- d %>%
    filter(region != mainReg, scenario != "historical") %>%
    droplevels()
  
  dRegiHist <- d %>%
    filter(region != mainReg, scenario == "historical") %>%
    droplevels()
  
  regions <- levels(dRegiScen$region)
  
  # Check if there is any data to plot
  if (nrow(dMainScen) == 0) {
    warning("Nothing to plot.", call. = FALSE)
    return(invisible(NULL))
  }
  
  label <- paste0("(", paste0(levels(d$unit), collapse = ","), ")")
  
  p2 <- dRegiScen %>%
    ggplot(aes(x = period, y = value, color = region)) +
    geom_line(aes(linetype = scenario)) +
    geom_point(data = dRegiHist, aes(shape = model)) +
    geom_line(data = dRegiHist, aes(group = paste0(model, region)), alpha = 0.5) +
    facet_wrap(~ variable, scales = scales, nrow = nrowNum) +
    theme_minimal() +
    scale_color_manual(values = plotstyle(regions)) +
    expand_limits(y = 0) +
    ylab(label)
  
  print(p2)
  cat("\n\n")
}
```

### Load factor
#### Pass other
```{r}
vars <- as.character(unique(data$variable))
items <- vars[grepl("Load factor \\(raw\\)\\|.*", vars)]
itemsSplit <- items[grepl(".*Pass.*", items) & !grepl(".*Four Wheelers.*|.*Two Wheelers.*|.*Three Wheelers.*|.*Non-motorized.*", items)]
plotData <- data %>%
  filter(variable %in% itemsSplit) %>%
  mutate(variable = gsub("(Load factor raw|\\|Transport|\\|Pass\\||\\|Bunkers)", "", variable))
itemsSplit <- unique(plotData$variable)
showTransportInputMultiLinePlots(plotData, itemsSplit, nrowNum = ceiling(length(itemsSplit) / 5))
```

#### Pass Four Wheelers
```{r}
itemsSplit <- items[grepl(".*Four Wheelers.*", items)]
plotData <- data %>%
  filter(variable %in% itemsSplit) %>%
  mutate(variable = gsub("^.*\\|Four Wheelers\\|[A-Za-z]+\\|", "", variable))
itemsSplit <- unique(plotData$variable)
showTransportInputMultiLinePlots(plotData, itemsSplit, nrowNum = ceiling(length(itemsSplit) / 6))
```

#### Pass Two Wheelers
```{r}
itemsSplit <- items[grepl(".*Two Wheelers.*", items)]
plotData <- data %>%
  filter(variable %in% itemsSplit) %>%
  mutate(variable = gsub("^.*\\|Two Wheelers\\|", "", variable))
itemsSplit <- unique(plotData$variable)
showTransportInputMultiLinePlots(plotData, itemsSplit, nrowNum = 2)
```

#### Freight other
```{r}
itemsSplit <- items[grepl(".*Freight.*", items) & !grepl(".*Truck.*", items)]
plotData <- data %>%
  filter(variable %in% itemsSplit) %>%
  mutate(variable = gsub("(\\|Transport|\\|Pass|\\|Bunkers)", "", variable))
itemsSplit <- unique(plotData$variable)
showTransportInputMultiLinePlots(plotData, itemsSplit, nrowNum = 2)
```

#### Freight Trucks
```{r}
itemsSplit <- items[grepl(".*Freight.*", items) & grepl(".*Truck.*", items)]
plotData <- data %>%
  filter(variable %in% itemsSplit) %>%
  mutate(variable = gsub("^.*\\|Road\\|[A-Za-z]+\\|", "", variable))
itemsSplit <- unique(plotData$variable)
showTransportInputMultiLinePlots(plotData, itemsSplit, nrowNum = ceiling(length(itemsSplit) / 6))
```

### Energy intensity
#### Pass other
```{r}
items <- vars[grepl("Energy intensity \\(raw\\)\\|.*", vars)]
itemsSplit <- items[grepl(".*Pass.*", items) & !grepl(".*Four Wheelers.*|.*Two Wheelers.*|.*Non-motorized.*", items)]
plotData <- data %>%
  filter(variable %in% itemsSplit) %>%
  mutate(variable = gsub("(Energy intensity (raw)|\\|Transport|\\|Pass\\||\\|Bunkers)", "", variable))
itemsSplit <- unique(plotData$variable)
showTransportInputMultiLinePlots(plotData, itemsSplit, nrowNum = ceiling(length(itemsSplit) / 5))
```

#### Pass Four Wheelers
```{r}
itemsSplit <- items[grepl(".*Four Wheelers.*", items)]
plotData <- data %>%
  filter(variable %in% itemsSplit) %>%
  mutate(variable = gsub("^.*\\|Four Wheelers\\|[A-Za-z]+\\|", "", variable))
itemsSplit <- unique(plotData$variable)
showTransportInputMultiLinePlots(plotData, itemsSplit, nrowNum = ceiling(length(itemsSplit) / 6))
```

#### Pass Two Wheelers
```{r}
itemsSplit <- items[grepl(".*Two Wheelers.*", items)]
plotData <- data %>%
  filter(variable %in% itemsSplit) %>%
  mutate(variable = gsub("^.*\\|Two Wheelers\\|", "", variable))
itemsSplit <- unique(plotData$variable)
showTransportInputMultiLinePlots(plotData, itemsSplit, nrowNum = 2)
```

#### Freight other
```{r}
itemsSplit <- items[grepl(".*Freight.*", items) & !grepl(".*Truck.*", items)]
plotData <- data %>%
  filter(variable %in% itemsSplit) %>%
  mutate(variable = gsub("(\\|Transport|\\|Pass|\\|Bunkers)", "", variable))
itemsSplit <- unique(plotData$variable)
showTransportInputMultiLinePlots(plotData, itemsSplit, nrowNum = 2)
```

#### Freight Trucks
```{r}
itemsSplit <- items[grepl(".*Freight.*", items) & grepl(".*Truck.*", items)]
plotData <- data %>%
  filter(variable %in% itemsSplit) %>%
  mutate(variable = gsub("^.*\\|Road\\|[A-Za-z]+\\|", "", variable))
itemsSplit <- unique(plotData$variable)
showTransportInputMultiLinePlots(plotData, itemsSplit, nrowNum = ceiling(length(itemsSplit) / 6))
```

### Annual mileage
#### Cars
```{r}
items <- vars[grepl(".*Annual mileage.*", vars)]
itemsSplit <- items[grepl(".*Four Wheelers.*", items)]
plotData <- data %>%
  filter(variable %in% itemsSplit) %>%
  mutate(variable = gsub("^.*\\|Four Wheelers\\|[A-Za-z]+\\|", "", variable))
itemsSplit <- unique(plotData$variable)
showTransportInputMultiLinePlots(plotData, itemsSplit, nrowNum = ceiling(length(itemsSplit) / 6))
```

#### Busses
```{r}
itemsSplit <- items[grepl(".*Bus.*", items)]
plotData <- data %>%
  filter(variable %in% itemsSplit) %>%
  mutate(variable = gsub("^.*\\|Road\\|", "", variable))
itemsSplit <- unique(plotData$variable)
showTransportInputMultiLinePlots(plotData, itemsSplit, nrowNum = ceiling(length(itemsSplit) / 6))
```

#### Trucks
```{r}
itemsSplit <- items[grepl(".*Freight.*", items) & grepl(".*Truck.*", items)]
plotData <- data %>%
  filter(variable %in% itemsSplit) %>%
  mutate(variable = gsub("^.*\\|Road\\|[A-Za-z]+\\|", "", variable))
itemsSplit <- as.character(unique(plotData$variable))
showTransportInputMultiLinePlots(plotData, itemsSplit, nrowNum = ceiling(length(itemsSplit )/6))
```  

### Purchase Price Cars, Trucks and Busses
#### Cars
```{r}
items <- vars[grepl(".*Purchase Price.*", vars)]
itemsSplit <- items[grepl(".*Four Wheelers.*", items)]
plotData <- data %>%
  filter(variable %in% itemsSplit) %>%
  mutate(variable = gsub("^.*\\|Four Wheelers\\|[A-Za-z]+\\|", "", variable))
itemsSplit <- as.character(unique(plotData$variable))
showTransportInputMultiLinePlots(plotData, itemsSplit, nrowNum = ceiling(length(itemsSplit )/6))
```  

#### Busses
```{r}
itemsSplit <- items[grepl(".*Bus.*", items)]
plotData <- data %>%
  filter(variable %in% itemsSplit) %>%
  mutate(variable = gsub("^.*\\|Road\\|", "", variable))
itemsSplit <- as.character(unique(plotData$variable))
showTransportInputMultiLinePlots(plotData, itemsSplit, nrowNum = ceiling(length(itemsSplit )/6))
```  

#### Trucks
```{r}
itemsSplit <- items[grepl(".*Freight.*", items) & grepl(".*Truck.*", items)]
plotData <- data %>%
  filter(variable %in% itemsSplit) %>%
  mutate(variable = gsub("^.*\\|Road\\|[A-Za-z]+\\|", "", variable))
itemsSplit <- as.character(unique(plotData$variable))
showTransportInputMultiLinePlots(plotData, itemsSplit, nrowNum = ceiling(length(itemsSplit )/6))
```  

### Time value costs
#### Pass other
```{r}
items <- vars[grepl("^Time value costs\\|.*", vars)]
itemsSplit <- items[grepl(".*Pass.*", items) & !grepl(".*Four Wheelers.*", items) & !grepl(".*Two Wheelers.*", items)]
plotData <- data %>%
  filter(variable %in% itemsSplit) %>%
  mutate(variable = gsub("(Time value costs|\\|Transport|\\|Pass\\||\\|Bunkers)", "", variable))
itemsSplit <- as.character(unique(plotData$variable))
showTransportInputMultiLinePlots(plotData, itemsSplit, nrowNum = ceiling(length(itemsSplit )/5))
```  

#### Pass Four Wheelers
```{r}
itemsSplit <- items[grepl(".*Four Wheelers.*", items)]
plotData <- data %>%
  filter(variable %in% itemsSplit) %>%
  mutate(variable = gsub("^.*\\|Four Wheelers\\|[A-Za-z]+\\|", "", variable))
itemsSplit <- as.character(unique(plotData$variable))
showTransportInputMultiLinePlots(plotData, itemsSplit, nrowNum = ceiling(length(itemsSplit )/6))
```  

#### Pass Two Wheelers
```{r}
itemsSplit <- items[grepl(".*Two Wheelers.*", items)]
plotData <- data %>%
  filter(variable %in% itemsSplit) %>%
  mutate(variable = gsub("^.*\\|Two Wheelers\\|", "", variable))
itemsSplit <- as.character(unique(plotData$variable))
showTransportInputMultiLinePlots(plotData, itemsSplit, nrowNum = 2)
```  

## Scenario specific input data
### Annualized TCO for new sales
#### Capital costs
##### Pass other
```{r}
items <- vars[grepl("TCO sales Capital costs\\|.*", vars)]
itemsSplit <- items[grepl(".*Pass.*", items) & !grepl(".*Four Wheelers.*", items) & !grepl(".*Two Wheelers.*", items)& !grepl(".*Non-motorized.*", items)]
plotData <- data %>%
  filter(variable %in% itemsSplit) %>%
  mutate(variable = gsub("(TCO sales Capital costs|\\|Transport|\\|Pass\\||\\|Bunkers)", "", variable))
itemsSplit <- as.character(unique(plotData$variable))
showTransportInputMultiLinePlots(plotData, itemsSplit, nrowNum = ceiling(length(itemsSplit )/5))
```  

##### Pass Four Wheelers
```{r}
itemsSplit <- items[grepl(".*Four Wheelers.*", items)]
plotData <- data %>%
  filter(variable %in% itemsSplit) %>%
  mutate(variable = gsub("^.*\\|Four Wheelers\\|[A-Za-z]+\\|", "", variable))
itemsSplit <- as.character(unique(plotData$variable))
showTransportInputMultiLinePlots(plotData, itemsSplit, nrowNum = ceiling(length(itemsSplit )/6))
```  

##### Pass Two Wheelers
```{r}
itemsSplit <- items[grepl(".*Two Wheelers.*", items)]
plotData <- data %>%
  filter(variable %in% itemsSplit) %>%
  mutate(variable = gsub("^.*\\|Two Wheelers\\|", "", variable))
itemsSplit <- as.character(unique(plotData$variable))
showTransportInputMultiLinePlots(plotData, itemsSplit, nrowNum = 2)
```  

##### Freight other
```{r}
itemsSplit <- items[grepl(".*Freight.*", items) & !grepl(".*Truck.*", items)]
plotData <- data %>%
  filter(variable %in% itemsSplit) %>%
  mutate(variable = gsub("(\\|Transport|\\|Pass|\\|Bunkers)", "", variable))
itemsSplit <- as.character(unique(plotData$variable))
showTransportInputMultiLinePlots(plotData, itemsSplit, nrowNum = 2)
```  

##### Freight Trucks
```{r}
itemsSplit<- items[grepl(".*Freight.*", items) & grepl(".*Truck.*", items)]
plotData <- data %>%
  filter(variable %in% itemsSplit) %>%
  mutate(variable = gsub("^.*\\|Road\\|[A-Za-z]+\\|", "", variable))
itemsSplit <- as.character(unique(plotData$variable))
showTransportInputMultiLinePlots(plotData, itemsSplit, nrowNum = ceiling(length(itemsSplit )/6))
```  

#### Operating costs (non-fuel)
##### Pass other
```{r}
items <- vars[grepl("TCO sales Operating costs \\(total non-fuel\\)\\|.*", vars)]
itemsSplit <- items[grepl(".*Pass.*", items) & !grepl(".*Four Wheelers.*", items) & !grepl(".*Two Wheelers.*", items)& !grepl(".*Non-motorized.*", items)]
plotData <- data %>%
  filter(variable %in% itemsSplit) %>%
  mutate(variable = gsub("(TCO sales Operating costs \\(total non-fuel\\)|\\|Transport|\\|Pass\\||\\|Bunkers)", "", variable))
itemsSplit <- as.character(unique(plotData$variable))
showTransportInputMultiLinePlots(plotData, itemsSplit, nrowNum = ceiling(length(itemsSplit )/5))
```  

##### Pass Four Wheelers
```{r}
itemsSplit <- items[grepl(".*Four Wheelers.*", items)]
plotData <- data %>%
  filter(variable %in% itemsSplit) %>%
  mutate(variable = gsub("^.*\\|Four Wheelers\\|[A-Za-z]+\\|", "", variable))
itemsSplit <- as.character(unique(plotData$variable))
showTransportInputMultiLinePlots(plotData, itemsSplit, nrowNum = ceiling(length(itemsSplit )/6))
```  

##### Pass Two Wheelers
```{r}
itemsSplit <- items[grepl(".*Two Wheelers.*", items)]
plotData <- data %>%
  filter(variable %in% itemsSplit) %>%
  mutate(variable = gsub("^.*\\|Two Wheelers\\|", "", variable))
itemsSplit <- as.character(unique(plotData$variable))
showTransportInputMultiLinePlots(plotData, itemsSplit, nrowNum = 2)
```  

##### Freight other
```{r}
itemsSplit <- items[grepl(".*Freight.*", items) & !grepl(".*Truck.*", items)]
plotData <- data %>%   filter(variable %in% itemsSplit) %>%   mutate(variable = gsub("(\\|Transport|\\|Pass|\\|Bunkers)", "", variable))
itemsSplit <- as.character(unique(plotData$variable))
showTransportInputMultiLinePlots(plotData, itemsSplit, nrowNum = 2)
```  

##### Freight Trucks
```{r}
itemsSplit<- items[grepl(".*Freight.*", items) & grepl(".*Truck.*", items)]
plotData <- data %>%   filter(variable %in% itemsSplit) %>%   mutate(variable = gsub("^.*\\|Road\\|[A-Za-z]+\\|", "", variable))
itemsSplit <- as.character(unique(plotData$variable))
showTransportInputMultiLinePlots(plotData, itemsSplit, nrowNum = ceiling(length(itemsSplit )/6))
```  

#### Fuel costs
##### Pass other
```{r}
items <- vars[grepl("TCO sales Fuel costs\\|.*", vars)]
itemsSplit <- items[grepl(".*Pass.*", items) & !grepl(".*Four Wheelers.*", items) & !grepl(".*Two Wheelers.*", items)& !grepl(".*Non-motorized.*", items)]
plotData <- data %>%   filter(variable %in% itemsSplit) %>%   mutate(variable = gsub("(TCO sales Fuel costs|\\|Transport|\\|Pass\\||\\|Bunkers)", "", variable))
itemsSplit <- as.character(unique(plotData$variable))
showTransportInputMultiLinePlots(plotData, itemsSplit, nrowNum = ceiling(length(itemsSplit )/5))
```  

##### Pass Four Wheelers
```{r}
itemsSplit <- items[grepl(".*Four Wheelers.*", items)]
plotData <- data %>%   filter(variable %in% itemsSplit) %>%   mutate(variable = gsub("^.*\\|Four Wheelers\\|[A-Za-z]+\\|", "", variable))
itemsSplit <- as.character(unique(plotData$variable))
showTransportInputMultiLinePlots(plotData, itemsSplit, nrowNum = ceiling(length(itemsSplit )/6))
```  

##### Pass Two Wheelers
```{r}
itemsSplit <- items[grepl(".*Two Wheelers.*", items)]
plotData <- data %>%   filter(variable %in% itemsSplit) %>%   mutate(variable = gsub("^.*\\|Two Wheelers\\|", "", variable))
itemsSplit <- as.character(unique(plotData$variable))
showTransportInputMultiLinePlots(plotData, itemsSplit, nrowNum = 2)
```  

##### Freight other
```{r}
itemsSplit <- items[grepl(".*Freight.*", items) & !grepl(".*Truck.*", items)]
plotData <- data %>%   filter(variable %in% itemsSplit) %>%   mutate(variable = gsub("(\\|Transport|\\|Pass|\\|Bunkers)", "", variable))
itemsSplit <- as.character(unique(plotData$variable))
showTransportInputMultiLinePlots(plotData, itemsSplit, nrowNum = 2)
```  

##### Freight Trucks
```{r}
itemsSplit<- items[grepl(".*Freight.*", items) & grepl(".*Truck.*", items)]
plotData <- data %>%   filter(variable %in% itemsSplit) %>%   mutate(variable = gsub("^.*\\|Road\\|[A-Za-z]+\\|", "", variable))
itemsSplit <- as.character(unique(plotData$variable))
showTransportInputMultiLinePlots(plotData, itemsSplit, nrowNum = ceiling(length(itemsSplit )/6))
```  

### Scenario specific load factor
#### Pass other
```{r}
vars <- as.character(unique(data$variable))
items <- vars[grepl("Load factor\\|.*", vars)]
itemsSplit <- items[grepl(".*Pass.*", items) & !grepl(".*Four Wheelers.*", items) & !grepl(".*Two Wheelers.*", items)& !grepl(".*Non-motorized.*", items)]
plotData <- data %>%   filter(variable %in% itemsSplit) %>%   mutate(variable = gsub("(Load factor|\\|Transport|\\|Pass\\||\\|Bunkers)", "", variable))
itemsSplit <- as.character(unique(plotData$variable))
showTransportInputMultiLinePlots(plotData, itemsSplit, nrowNum = ceiling(length(itemsSplit )/5))
```  

#### Pass Four Wheelers
```{r}
itemsSplit <- items[grepl(".*Four Wheelers.*", items)]
plotData <- data %>%   filter(variable %in% itemsSplit) %>%   mutate(variable = gsub("^.*\\|Four Wheelers\\|[A-Za-z]+\\|", "", variable))
itemsSplit <- as.character(unique(plotData$variable))
showTransportInputMultiLinePlots(plotData, itemsSplit, nrowNum = ceiling(length(itemsSplit )/6))
```  

#### Pass Two Wheelers
```{r}
itemsSplit <- items[grepl(".*Two Wheelers.*", items)]
plotData <- data %>%   filter(variable %in% itemsSplit) %>%   mutate(variable = gsub("^.*\\|Two Wheelers\\|", "", variable))
itemsSplit <- as.character(unique(plotData$variable))
showTransportInputMultiLinePlots(plotData, itemsSplit, nrowNum = 2)
```  

#### Freight other
```{r}
itemsSplit <- items[grepl(".*Freight.*", items) & !grepl(".*Truck.*", items)]
plotData <- data %>%   filter(variable %in% itemsSplit) %>%   mutate(variable = gsub("(\\|Transport|\\|Pass|\\|Bunkers)", "", variable))
itemsSplit <- as.character(unique(plotData$variable))
showTransportInputMultiLinePlots(plotData, itemsSplit, nrowNum = 2)
```  

#### Freight Trucks
```{r}
itemsSplit<- items[grepl(".*Freight.*", items) & grepl(".*Truck.*", items)]
plotData <- data %>%   filter(variable %in% itemsSplit) %>%   mutate(variable = gsub("^.*\\|Road\\|[A-Za-z]+\\|", "", variable))
itemsSplit <- as.character(unique(plotData$variable))
showTransportInputMultiLinePlots(plotData, itemsSplit, nrowNum = ceiling(length(itemsSplit )/6))
```  

### Scenario specific energy intensity
#### Pass other
```{r}
items <- vars[grepl("Energy intensity sales\\|.*", vars)]
itemsSplit <- items[grepl(".*Pass.*", items) & !grepl(".*Four Wheelers.*", items) & !grepl(".*Two Wheelers.*", items)& !grepl(".*Non-motorized.*", items)]
plotData <- data %>%   filter(variable %in% itemsSplit) %>%   mutate(variable = gsub("(Energy intensity sales|\\|Transport|\\|Pass\\||\\|Bunkers)", "", variable))
itemsSplit <- as.character(unique(plotData$variable))
showTransportInputMultiLinePlots(plotData, itemsSplit, nrowNum = ceiling(length(itemsSplit )/5))
```  

#### Pass Four Wheelers
```{r}
itemsSplit <- items[grepl(".*Four Wheelers.*", items)]
plotData <- data %>%   filter(variable %in% itemsSplit) %>%   mutate(variable = gsub("^.*\\|Four Wheelers\\|[A-Za-z]+\\|", "", variable))
itemsSplit <- as.character(unique(plotData$variable))
showTransportInputMultiLinePlots(plotData, itemsSplit, nrowNum = ceiling(length(itemsSplit )/6))
```  

#### Pass Two Wheelers
```{r}
itemsSplit <- items[grepl(".*Two Wheelers.*", items)]
plotData <- data %>%   filter(variable %in% itemsSplit) %>%   mutate(variable = gsub("^.*\\|Two Wheelers\\|", "", variable))
itemsSplit <- as.character(unique(plotData$variable))
showTransportInputMultiLinePlots(plotData, itemsSplit, nrowNum = 2)
```  

#### Freight other
```{r}
itemsSplit <- items[grepl(".*Freight.*", items) & !grepl(".*Truck.*", items)]
plotData <- data %>%   filter(variable %in% itemsSplit) %>%   mutate(variable = gsub("(\\|Transport|\\|Pass|\\|Bunkers)", "", variable))
itemsSplit <- as.character(unique(plotData$variable))
showTransportInputMultiLinePlots(plotData, itemsSplit, nrowNum = 2)
```  

#### Freight Trucks
```{r}
itemsSplit<- items[grepl(".*Freight.*", items) & grepl(".*Truck.*", items)]
plotData <- data %>%   filter(variable %in% itemsSplit) %>%   mutate(variable = gsub("^.*\\|Road\\|[A-Za-z]+\\|", "", variable))
itemsSplit <- as.character(unique(plotData$variable))
showTransportInputMultiLinePlots(plotData, itemsSplit, nrowNum = ceiling(length(itemsSplit )/6))
```  

### Preference trends
#### sector-Subsector 1
##### Pass
```{r}
items <- vars[grepl("Preference\\|S1S\\|.*", vars)]
itemsSplit <- items[grepl(".*Pass.*", items)]
plotData <- data %>%   filter(variable %in% itemsSplit) %>%   mutate(variable = gsub("(Preference\\|S1S|\\|Transport|\\|Pass\\||\\|Bunkers)", "", variable))
itemsSplit <- as.character(unique(plotData$variable))
showTransportInputMultiLinePlots(plotData, itemsSplit, nrowNum = ceiling(length(itemsSplit )/5))
```  

##### Freight
```{r}
items <- vars[grepl("Preference\\|S1S\\|.*", vars)]
itemsSplit <- items[grepl(".*Freight.*", items)]
plotData <- data %>%   filter(variable %in% itemsSplit) %>%   mutate(variable = gsub("(Preference\\|S1S|\\|Transport|\\|Freight\\||\\|Bunkers)", "", variable))
itemsSplit <- as.character(unique(plotData$variable))
showTransportInputMultiLinePlots(plotData, itemsSplit, nrowNum = ceiling(length(itemsSplit )/5))
```  

#### Subsector 1 - Subsector 2
```{r}
items <- vars[grepl("Preference\\|S2S1\\|.*", vars)]
itemsSplit <- items[grepl(".*Pass.*", items) & grepl(".*Bus.*|.*LDV.*", items)]
plotData <- data %>%   filter(variable %in% itemsSplit) %>%   mutate(variable = gsub("(Preference\\|S2S1|\\|Transport|\\|Pass\\||\\|Bunkers)", "", variable))
itemsSplit <- as.character(unique(plotData$variable))
showTransportInputMultiLinePlots(plotData, itemsSplit, nrowNum = ceiling(length(itemsSplit)/5))
``` 

#### Subsector 2 - Subsector 3
```{r}
items <- vars[grepl("Preference\\|S3S2\\|.*", vars)]
itemsSplit <- items[grepl(".*Pass.*", items) & grepl(".*LDV.*", items)]
plotData <- data %>%   filter(variable %in% itemsSplit) %>%   mutate(variable = gsub("(Preference\\|S3S2|\\|Transport|\\|Pass\\||\\|Bunkers)", "", variable))
itemsSplit <- as.character(unique(plotData$variable))
showTransportInputMultiLinePlots(plotData, itemsSplit, nrowNum = ceiling(length(itemsSplit)/5))
``` 

#### Subsector 3 - Vehicle
##### Pass
```{r}
items <- vars[grepl("Preference\\|VS3\\|.*", vars)]
itemsSplit <- items[grepl(".*Pass.*", items)& grepl(".*LDV.*", items)]
plotData <- data %>%   filter(variable %in% itemsSplit) %>%   mutate(variable = gsub("^.*\\|LDV\\|", "", variable))
itemsSplit <- as.character(unique(plotData$variable))
showTransportInputMultiLinePlots(plotData, itemsSplit, nrowNum = ceiling(length(itemsSplit )/5))
```  

##### Freight
```{r}
items <- vars[grepl("Preference\\|VS3\\|.*", vars)]
itemsSplit <- items[grepl(".*Freight.*", items)& grepl(".*Road.*", items)]
plotData <- data %>%   filter(variable %in% itemsSplit) %>%   mutate(variable = gsub("^.*\\|Road\\|", "", variable))
itemsSplit <- as.character(unique(plotData$variable))
showTransportInputMultiLinePlots(plotData, itemsSplit, nrowNum = ceiling(length(itemsSplit )/5))
```  

#### Vehicle - Fuel
#### Pass other
```{r}
items <- vars[grepl("Preference\\|FV\\|.*", vars)]
itemsSplit <- items[grepl(".*Pass.*", items) & !grepl(".*Four Wheelers.*", items) & !grepl(".*Two Wheelers.*", items)& !grepl(".*(Walk|Cycle).*", items)]
plotData <- data %>%   filter(variable %in% itemsSplit) %>%   mutate(variable = gsub("(Preference\\|FV|\\|Transport|\\|Pass\\||\\|Bunkers)", "", variable))
itemsSplit <- as.character(unique(plotData$variable))
showTransportInputMultiLinePlots(plotData, itemsSplit, nrowNum = ceiling(length(itemsSplit )/5))
```  

##### Pass Two Wheelers
```{r}
itemsSplit <- items[grepl(".*Two Wheelers.*", items)]
plotData <- data %>%   filter(variable %in% itemsSplit) %>%   mutate(variable = gsub("^.*\\|Two Wheelers\\|", "", variable))
itemsSplit <- as.character(unique(plotData$variable))
showTransportInputMultiLinePlots(plotData, itemsSplit, nrowNum = 2)
```  

#### Freight other
```{r}
items <- vars[grepl("Preference\\|FV\\|.*", vars)]
itemsSplit <- items[grepl(".*Freight.*", items) & !grepl(".*Road.*", items)]
plotData <- data %>%   filter(variable %in% itemsSplit) %>%   mutate(variable = gsub("(Preference\\|FV|\\|Transport|\\|Freight\\||\\|Bunkers)", "", variable))
itemsSplit <- as.character(unique(plotData$variable))
showTransportInputMultiLinePlots(plotData, itemsSplit, nrowNum = ceiling(length(itemsSplit )/5))
```  

##### Freight Trucks
```{r}
itemsSplit<- items[grepl("Preference\\|FV\\|.*", items) & grepl(".*Truck.*", items)]
plotData <- data %>%   filter(variable %in% itemsSplit) %>%   mutate(variable = gsub("Preference\\|FV\\|Transport\\|Freight\\|Road\\|", "", variable))
itemsSplit <- as.character(unique(plotData$variable))
showTransportInputMultiLinePlots(plotData, itemsSplit, nrowNum = ceiling(length(itemsSplit )/6))
```  

### GDP
```{r}
items <- vars[grepl(".*GDP.*", vars)]
showMultiLinePlots(data, items, nrowNum = 2)
```
