# Energy Services

## Passenger
### Energy Services by mode 
#### Without bunkers
```{r}
totWoBunk <- "ES|Transport edge|Pass"
items <- c(
    "ES|Transport|Pass|Domestic Aviation",
    "ES|Transport|Pass|Rail|HSR",
    "ES|Transport|Pass|Rail|non-HSR",
    "ES|Transport|Pass|Road|Bus",
    "ES|Transport|Pass|Road|LDV|Four Wheelers",
    "ES|Transport|Pass|Road|LDV|Two Wheelers",
    "ES|Transport|Pass|Non-motorized|Walk",
    "ES|Transport|Pass|Non-motorized|Cycle"
  )
showAreaAndBarPlots(data, items, totWoBunk, orderVars = "user")
showAreaAndBarPlots(data, items, totWoBunk, fill = TRUE, orderVars = "user")
```

#### With bunkers
```{r}
totBunk <- "ES|Transport|Pass with bunkers"
items <- c(
    "ES|Transport|Bunkers|Pass|International Aviation",
    "ES|Transport|Pass|Domestic Aviation",
    "ES|Transport|Pass|Rail|HSR",
    "ES|Transport|Pass|Rail|non-HSR",
    "ES|Transport|Pass|Road|Bus",
    "ES|Transport|Pass|Road|LDV|Four Wheelers",
    "ES|Transport|Pass|Road|LDV|Two Wheelers",
    "ES|Transport|Pass|Non-motorized|Walk",
    "ES|Transport|Pass|Non-motorized|Cycle"
  )
showAreaAndBarPlots(data, items, totBunk,  orderVars = "user")
showAreaAndBarPlots(data, items, totBunk, fill = TRUE, orderVars = "user")
showLinePlots(data, totBunk)
walk(c("ES|Transport|Pass|Aviation", totWoBunk, items[1:5], "ES|Transport|Pass|Road|LDV", items[6:9]),
     showLinePlots, data = data)
```

#### Four Wheelers
```{r}
tot <- "ES|Transport|Pass|Road|LDV|Four Wheelers"
items <- c(
       "ES|Transport|Pass|Road|LDV|Four Wheelers|Large",
       "ES|Transport|Pass|Road|LDV|Four Wheelers|Medium",
       "ES|Transport|Pass|Road|LDV|Four Wheelers|Small"
)

showAreaAndBarPlots(data, items, tot, orderVars = "user")
showAreaAndBarPlots(data, items, tot, fill = TRUE,  orderVars = "user")
```


```{r}
indicators <- c(
    "ES|Transport edge|Pass pCap",
    "ES|Transport|Pass with bunkers pCap",
    "ES|Transport|Pass|Aviation pCap",
    "ES|Transport|Bunkers|Pass|International Aviation pCap",
    "ES|Transport|Pass|Domestic Aviation pCap",
    "ES|Transport|Pass|Rail pCap",
    "ES|Transport|Pass|Road|LDV|Four Wheelers pCap",
    "ES|Transport|Pass|Rail|HSR pCap",
    "ES|Transport|Pass|Rail|non-HSR pCap",
    "ES|Transport|Pass|Road|Bus pCap",
    "ES|Transport|Pass|Road pCap",
    "ES|Transport|Pass|Road|LDV pCap",
    "ES|Transport|Pass|Road|LDV|Two Wheelers pCap",
    "ES|Transport|Pass|Non-motorized|Walk pCap",
    "ES|Transport|Pass|Non-motorized|Cycle pCap",
    "ES|Transport|Pass|Non-motorized pCap",
    "Stock|Transport|Pass|Road|LDV|Four Wheelers pCap"
    )
```

### Energy Service by mode line plot
```{r, results = 'asis'}
for (i in indicators) {
  i_total <- sub(" pCap", "", i)
  cat("\n\n####", i_total, "\n")
  showLinePlots(data, i_total)
}
```

### PerCap Energy Service by mode - line - Time domain
```{r, results = 'asis'}
for (i in indicators) {
  cat("\n\n####", sub("(\\|per-capita)|( pCap)", "", i), "\n")
  showLinePlots(data, i, scales = "fixed")
}
```

### PerCap Energy Service by mode - line - GDP domain
```{r}
items <- c(
    "ES|Transport edge|Pass pCap",
    "ES|Transport|Pass with bunkers pCap",
    "ES|Transport|Pass|Aviation pCap",
    "ES|Transport|Bunkers|Pass|International Aviation pCap",
    "ES|Transport|Pass|Domestic Aviation pCap",
    "ES|Transport|Pass|Rail pCap",
    "ES|Transport|Pass|Road|LDV|Four Wheelers pCap",
    "ES|Transport|Pass|Rail|HSR pCap",
    "ES|Transport|Pass|Rail|non-HSR pCap",
    "ES|Transport|Pass|Road pCap",
    "ES|Transport|Pass|Road|Bus pCap",
    "ES|Transport|Pass|Road|LDV pCap",
    "ES|Transport|Pass|Road|LDV|Two Wheelers pCap",
    "ES|Transport|Pass|Non-motorized|Walk pCap",
    "ES|Transport|Pass|Non-motorized|Cycle pCap",
    "ES|Transport|Pass|Non-motorized pCap",
    "Stock|Transport|Pass|Road|LDV|Four Wheelers pCap"
    )
#showMultiLinePlots(data, items[1:6], nrowNum = 2)
#showMultiLinePlots(data, items[7:12], nrowNum = 2)


showMultiLinePlots(data, items[1])
showMultiLinePlots(data, items[2])
showMultiLinePlots(data, items[3])
showMultiLinePlots(data, items[4])
showMultiLinePlots(data, items[5])
showMultiLinePlots(data, items[6])
showMultiLinePlots(data, items[7])
showMultiLinePlots(data, items[8])
showMultiLinePlots(data, items[9])
showMultiLinePlots(data, items[10])
showMultiLinePlots(data, items[11])
showMultiLinePlots(data, items[12])
showMultiLinePlots(data, items[13])
showMultiLinePlots(data, items[14])
showMultiLinePlots(data, items[15])
showMultiLinePlots(data, items[16])
showMultiLinePlots(data, items[17])

showMultiLinePlotsByVariable(data, items[c(1:7,11)], "GDP|PPP pCap", nrowNum = 2)
showMultiLinePlotsByVariable(data, items[c(8:15)], "GDP|PPP pCap", nrowNum = 2)
showMultiLinePlotsByVariable(data, items[c(16,17)], "GDP|PPP pCap", nrowNum = 2)
walk(items, showLinePlotsByVariable, data = data, xVar = "GDP|PPP pCap")
```

### Energy Service by technology
#### Four Wheelers
```{r}
tot <- "ES|Transport|Pass|Road|LDV|Four Wheelers"
items <- c(
       "ES|Transport|Pass|Road|LDV|Four Wheelers|BEV",
       "ES|Transport|Pass|Road|LDV|Four Wheelers|FCEV",
       "ES|Transport|Pass|Road|LDV|Four Wheelers|Hybrid electric",
       "ES|Transport|Pass|Road|LDV|Four Wheelers|Gases",
       "ES|Transport|Pass|Road|LDV|Four Wheelers|Liquids"
  )

showAreaAndBarPlots(data, items, tot, orderVars = "user")
showAreaAndBarPlots(data, items, tot, fill = TRUE, orderVars = "user")
```

#### LDV 2-Wheelers
```{r}
tot <- "ES|Transport|Pass|Road|LDV|Two Wheelers"
items <- c(
     "ES|Transport|Pass|Road|LDV|Two Wheelers|BEV",
     "ES|Transport|Pass|Road|LDV|Two Wheelers|Liquids"
  )

showAreaAndBarPlots(data, items, tot, orderVars = "user")
showAreaAndBarPlots(data, items, tot, fill = TRUE, orderVars = "user")
```

#### Busses
```{r}
tot <- "ES|Transport|Pass|Road|Bus"
items <- c(
       "ES|Transport|Pass|Road|Bus|BEV",
       "ES|Transport|Pass|Road|Bus|FCEV",
       "ES|Transport|Pass|Road|Bus|Gases",
       "ES|Transport|Pass|Road|Bus|Liquids"
  )

showAreaAndBarPlots(data, items, tot, orderVars = "user")
showAreaAndBarPlots(data, items, tot, fill = TRUE, orderVars = "user")
```

## Freight 
### Energy Services by mode 
#### Without bunkers
```{r}
totWoBunk <- "ES|Transport edge|Freight"
items <- c(
      "ES|Transport|Freight|Domestic Shipping",
      "ES|Transport|Freight|Rail",
      "ES|Transport|Freight|Road"
  )
showAreaAndBarPlots(data, items, totWoBunk, orderVars = "user")
showAreaAndBarPlots(data, items, totWoBbunk, fill = TRUE, orderVars = "user")
```

#### With bunkers
```{r}
totBunk <- "ES|Transport|Freight with bunkers"
items <- c(
      "ES|Transport|Bunkers|Freight|International Shipping",
      "ES|Transport|Freight|Domestic Shipping",
      "ES|Transport|Freight|Rail",
      "ES|Transport|Freight|Road"
  )
showAreaAndBarPlots(data, items, totBunk, orderVars = "user")
showAreaAndBarPlots(data, items, totBunk, fill = TRUE, orderVars = "user")
showLinePlots(data, totBunk)
walk(items, showLinePlots, data = data)
```

#### Trucks
```{r}
tot <- "ES|Transport|Freight|Road"
items <- c(
       "ES|Transport|Freight|Road|Heavy|Truck(40t)",
       "ES|Transport|Freight|Road|Heavy|Truck(26t)",
       "ES|Transport|Freight|Road|Heavy|Truck(18t)",
       "ES|Transport|Freight|Road|Light|Truck(7_5t)",
       "ES|Transport|Freight|Road|Light|Truck(0-3_5t)"
  )

showAreaAndBarPlots(data, items, tot, orderVars = "user")
showAreaAndBarPlots(data, items, tot, fill = TRUE, orderVars = "user")
```


```{r}
indicators <- c(
      "ES|Transport edge|Freight pCap",
      "ES|Transport|Freight with bunkers pCap",
      "ES|Transport|Bunkers|Freight|International Shipping pCap",
      "ES|Transport|Freight|Domestic Shipping pCap",
      "ES|Transport|Freight|Rail pCap",
      "ES|Transport|Freight|Road pCap"
    )
```

### Per Capita - Energy Service by mode - with bunkers Time domain
```{r, results = 'asis'}
for (i in indicators) {
  cat("\n\n####", sub("(\\|per-capita)|( pCap)", "", i), "\n")
  showLinePlots(data, i, scales = "fixed")
}
```

### Per Capita - Energy Service by mode - Freight with bunkers
```{r}

items <- c(
      "ES|Transport edge|Freight pCap",
      "ES|Transport|Freight with bunkers pCap",
      "ES|Transport|Bunkers|Freight|International Shipping pCap",
      "ES|Transport|Freight|Domestic Shipping pCap",
      "ES|Transport|Freight|Rail pCap",
      "ES|Transport|Freight|Road pCap"
    )
showMultiLinePlots(data, items, nrowNum = 2)
showMultiLinePlotsByVariable(data, items, "GDP|PPP pCap", nrowNum = 2)
walk(items, showLinePlotsByVariable, data = data, xVar = "GDP|PPP pCap")
```


### Energy Service by technology - Trucks
```{r}
tot <-  "ES|Transport|Freight|Road"
items <- c(
       "ES|Transport|Freight|Road|BEV",
       "ES|Transport|Freight|Road|FCEV",
       "ES|Transport|Freight|Road|Gases",
       "ES|Transport|Freight|Road|Liquids"
  )

showAreaAndBarPlots(data, items, tot, orderVars = "user")
showAreaAndBarPlots(data, items, tot, fill = TRUE, orderVars = "user")
```

